\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Role of nuclear medicine in breast cancer}
\author{Submitted By Lingamgunta saikumar}
\date{4, march 2022}

\begin{document}

\maketitle

\section{ continuation of Tc-99m Multigated Radionuclide Angiography}
Following radiopharmaceutical treatment, a planar detection, SPECT or combination is obtained. To 
visualize all parts of the left ventricular wall, the projection position includes vertical, side, and left
oblique (LAO) horizontal views with a caudal to better separate the left ventricle from the left atrium 
and facilitates accurate processing. Using an electrocardiogram, images are recorded simultaneously 
with the patient's heartbeat to monitor ventricular wall movement in the left and attenuation. Final 
result series consecutive or phase thinking to accurately measure left ventricular volume and 
visualize dyssynchrony. The addition of the SPECT-gated method detects three-dimensional serial 
images that better distinguish left and right ventricles without overlapping to calculate left and right 
combinations. parts of the ventricular ejection and examine the regional wall motion. Early detection 
of cardiotoxic findings in serial thinking allows timely intervention to prevent patient-related diseases 
or death from trastuzumab and anthracycline therapy. Global LV systolic and diastolic performance 
indicators using RNA have proven to be effective in early evaluation of functional changes after 
chemotherapy compared to baseline, emphasizes that serial imaging is important at all stages of 
treatment to assess patient prediction. activity in anthracycline-induced cardiotoxicity and more 
importantly, is the first indication of at risk for cardiovascular function. difficulty swallowing. Visual 
Photopenic Remuneration Halo in pre- and LAO predictions of an ERNA scan may indicate early 
stages of pericardial infarction and allow early intervention and treatment adjustment to reduce 
progression. 
Whole bone scan in metastatic disease :
Bone metastases are present in ~80% of four women metastatic disease that highlights 
breast speculation cancer cells to amethyst bone. If bone metastases found, average survival 
is between 2.1 and 6 years. Additionally, patients may experience a deterioration of their 
quality of life from related complications of metastatic disease. As a result, the first stage 
and the standard follow-up test recovery is important in improving quality of life as well 
survival. Whole-body bone (WB) examination a less expensive testing and not importing that
accurate measurement of disease burden is recommended and follow-up tests with 
symptoms or high risk patients.
\end{document}
